# Sponsors

## Sponsor Opportunities

Bioconductor is a non-profit organization that supports one of the most widely used data analysis tools in genomics. Bioconductor had [1,069,044 downloads (distinct IPs)](http://www.bioconductor.org/packages/stats/bioc/index.html) in 2022. Software packages are contributed by more than 1,200 community developers worldwide, totaling over half a million downloads per year.  

The conference is unique in that in addition to talks and poster session, the meeting features workshops which provide hands-on learning in Bioconductor. All conference materials (videos, slides, talks, posters, workshops) are published online such that the conference provides a rich resource for learning Bioconductor. 

### Interested in sponsoring EuroBioC2025?

Please contact <eurobioc@bioconductor.org>

**Your sponsorship will help increase diversity and representation at the European Bioconductor Conference 2025** by:

- Reducing registration costs for academic participants, trainees and especially students from countries outside CA, EEA, UK or US.
- Funding travel scholarships for students, trainees and postdoctoral fellows from countries outside CA, EEA, UK or US.
- Offering student diversity scholarships to increase participation of students and trainees with migration background. 
- Providing caregiver awards to assist with childcare or eldercare costs.
- Provide high quality live streaming of the talks and post-production and sharing of videos and conference materials.

**Four levels of sponsorship are available.** Sponsors of all levels may give a short talk and/or present a poster highlighting the scientific interests of their organization in the poster session; for this, sponsors are kindly requested to submit an abstract within the deadline.

```{r echo=FALSE}
url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTH6w9C1hF_umKXxAWtjXj5W-Jjz511mOgKXpgYfl-v_kqLzFKOoH9oJ5kvbYMCIQt8p_iIjntUU7VR/pub?gid=106633706&single=true&output=csv"
df <- read.csv(url, check.names=FALSE)
rownames(df) <- df[, 1]
df <- df[, -1]
names(df)[1] <- ""
library(kableExtra)
```

```{r results="asis", echo=FALSE}
kbl(df, row.names=FALSE, align=c("r", rep("c", ncol(df)-1))) |>
    kable_material() |>
    column_spec(1, width="66%") |>
    row_spec(seq(1, nrow(df), 2), 
        background="ghostwhite") |>
    cat()
```

