# Sponsors

[Bioconductor](https://bioconductor.org) is a non-profit organisation that supports one of the most widely used data analysis ecosystems in genomics.
Software packages are contributed by more than 1,200 community developers worldwide, totaling over 42 million downloads by [about 1 million distinct IP addresses](https://www.bioconductor.org/packages/stats/bioc/index.html) in 2023. 

The next edition of the European Bioconductor Conference (EuroBioC) will be held in Barcelona, Spain, at the [Barcelona Biomedical Research Park](https://prbb.org) on 17-19 September 2025.
We expect around 200 participants from the European and global bioinformatics community, coming from academia and industry.
We are welcoming bioinformaticians, method developers, practitioners incorporating R/Bioconductor into robust workflows, and researchers using these tools for biological and biomedical discovery. 

**Your sponsorship will help us provide a high-quality in-person event, and increase equity, diversity and inclusion at EuroBioC2025** by reducing registration costs and funding scholarships for students and other academic participants from lower income countries or with no other means of funding.

**Four levels of sponsorship are available.** 
Sponsors of all levels are invited to submit an abstract within the deadline, which will be subject to review alongside submissions by attendees.
Selected abstracts will be given the opportunity to give a short talk or present a poster that may highlight the scientific interests of the organisation, research applications of their product(s), etc.

\usepackage{amssymb}

```{r echo=FALSE}
url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTH6w9C1hF_umKXxAWtjXj5W-Jjz511mOgKXpgYfl-v_kqLzFKOoH9oJ5kvbYMCIQt8p_iIjntUU7VR/pub?gid=106633706&single=true&output=csv"
df <- read.csv(url, check.names=FALSE)
df[df == "X"] <- "$\\checkmark$"
library(kableExtra)
```

```{r results="asis", echo=FALSE}
kbl(df, row.names=FALSE, align=c("r", rep("c", ncol(df)-1))) |>
    kable_material() |>
    column_spec(1, width="66%") |>
    row_spec(seq(1, nrow(df), 2), 
        background="ghostwhite") |>
    cat()
```

